### 2018-05-21 README.Rmd
more detailed readme

# saaabstracts

The goal of saaabstracts is to help organise the program for the 2018 Society of American Archaeology meeting.

@@

The task of classification was done by using hierarchical cluster analysis on the keywords submitted by authors with their abstracts. We tried topic modelling the abstracts, but this did not give much discriminating power. A little manual handling was needed after the `hclust` results because we don't have an easy way to set the upper limit of a cluster size. Once the general submissions were grouped into sessions, then we could send them out to reviwers

@@

4. After the slots are filled, we do some checking to make sure we didn't lose any sessions or papers. This is important because the multiple knapsack algorithm may fail to sort all sessions if it cannot find an optimum solution.

5. Then we check for conflicts with special requests from the SAA, and relocate sessions if necessary. And then check again to ensure we haven't introduced any clashes.

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Title of compendium_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

You can install saaabstracts from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("benmarwick/saaabstracts")
```

>>>>

# confschedlr

The goal of confschedlr is to help organise the program for the 2018 Society of American Archaeology meeting.

@@

The task of classification was done by using hierarchical cluster analysis on the keywords submitted by authors with their abstracts. We tried topic modelling the abstracts, but this did not give much discriminating power. A little manual handling was needed after the `hclust` results because we don't have an easy way to set the upper limit of a cluster size. Once the general submissions were grouped into sessions, then we could send them out to reviwers. In the future this could be imporved by using a controlled vocabulary for keywords so we don't have so many synonyms to manually handle.

@@

4. After the slots are filled, we do some checking to make sure we didn't lose any sessions or papers. This is important because the multiple knapsack algorithm may fail to sort all sessions if it cannot find an optimum solution. 
5. Then we check for conflicts with special requests from the SAA, and relocate sessions if necessary. And then check again to ensure we haven't introduced any clashes.

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _confschedlr: An R package for scheduling conference sessions_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

You can install confschedlr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("benmarwick/confschedlr")
```
